Manhattan Plot

### 2021-09-08 code/manhattan_animated.Rmd
update code and fix bugs

```{r, echo = F, message = F, warning = F}
df_OR = read_csv("data/DF_OR_27.csv") %>%
  arrange(theme, id) %>%
  mutate (pos = row_number(),
          week = 27) %>%
  bind_rows(read_csv("data/DF_OR_32.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 32)) %>%
  bind_rows(read_csv("data/DF_OR_05.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 05)) %>%
  bind_rows(read_csv("data/DF_OR_07.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 07)) %>%
  bind_rows(read_csv("data/DF_OR_09.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 09)) %>%
  bind_rows(read_csv("data/DF_OR_11.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 11)) %>%
  bind_rows(read_csv("data/DF_OR_12.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 12)) %>%
  bind_rows(read_csv("data/DF_OR_15.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 15)) %>%
  bind_rows(read_csv("data/DF_OR_17.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 17)) %>%
  bind_rows(read_csv("data/DF_OR_19.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 19)) %>%
  bind_rows(read_csv("data/DF_OR_21.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 21)) %>%
  bind_rows(read_csv("data/DF_OR_24.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 24)) %>%
  bind_rows(read_csv("data/DF_OR_23.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 23)) %>%
  bind_rows(read_csv("data/DF_OR_26.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 26)) %>%
  bind_rows(read_csv("data/DF_OR_29.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 29)) %>%
  bind_rows(read_csv("data/DF_OR_30.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 30)) %>%
  bind_rows(read_csv("data/DF_OR_32.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 32)) %>%
  bind_rows(read_csv("data/DF_OR_02.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 02)) %>%
  bind_rows(read_csv("data/DF_OR_04.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 04)) %>%
  bind_rows(read_csv("data/DF_OR_14.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 14)) %>%
  bind_rows(read_csv("data/DF_OR_18.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 18)) %>%
  bind_rows(read_csv("data/DF_OR_31.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 31)) %>%
  bind_rows(read_csv("data/DF_OR_33.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 33)) %>%
  mutate(`is_OR_>1` = if_else(`is_OR_>1`, "OR", "1/OR"))
```

```{r}
df_OR %>%
  filter(week == 33) %>%
  arrange(OR) %>%
  mutate(pos2 = row_number()) %>%
  select(Variable, pos2) %>%
  inner_join(df_OR)
```

>>>>

```{r, echo = F, message = F, warning = F}
LOG_fact = read_csv("data/LOG_fact.csv", col_type = list(.default = col_factor()))
EMP_fact = read_csv("data/EMP_fact.csv", col_type = list(.default = col_factor()))
ACT_fact = read_csv("data/ACT_fact.csv", col_type = list(.default = col_factor()))
REV_fact = read_csv("data/REV_fact.csv", col_type = list(.default = col_factor()))
POP_fact = read_csv("data/POP_fact.csv", col_type = list(.default = col_factor()))
FOR_fact = read_csv("data/FOR_fact.csv", col_type = list(.default = col_factor()))
IMM_fact = read_csv("data/IMM_fact.csv", col_type = list(.default = col_factor()))
GEO_fact = read_csv("data/GEO_fact.csv", col_type = list(.default = col_factor()))
FAM_fact = read_csv("data/FAM_fact.csv", col_type = list(.default = col_factor()))
```

```{r, echo = F, message = F, warning = F}
binarisation = function(liste, q = 0.5){
  mediane = quantile(liste, q, na.rm = T)[[1]]
  return(as.factor(simplify2array(lapply(liste-mediane,
                                         function(x){if_else(x < 0, 0, 1)}))))
}

make_data_covid = function(wk){

  if (wk/10 <1){
    wk = paste0("0", wk)
  }

  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    mutate(codgeo = as.factor(commune_residence)) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    mutate(codgeo = as.factor(epci)) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
    plyr::rbind.fill(vacc_com)

  LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))

  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(LOG_OR_1107) = NULL
  # write_csv2(LOG_OR, "data/LOG_OR.csv")

  EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(EMP_OR_1107) = NULL
  # write_csv2(EMP_OR, "data/EMP_OR.csv")

  FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(FAM_OR_1107) = NULL
  # write_csv2(FAM_OR, "data/FAM_OR.csv")

  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(REV_OR_1107) = NULL
  # write_csv2(REV_OR, "data/REV_OR.csv")
